### 2016-01-23 p00-ch00-intro/intro.tex
Add the first draft of 'Samenvatting' in English

The core contributions of this thesis target at the intersection of object 
orientation, actor model, and concurrency.
We choose Java as the main programming language and as one of the mainstream 
object-oriented languages. 
We formalize a subset of Java and its concurrency API~\cite{jsr166} to 
facilitate formal verification and reasoning about it.
We create an abstract mapping from a concurrent-object modelling language, 
ABS~\cite{johnsen2012abs}, to programming semantics of Java concurrency. 
We provide the formal semantics of the mapping and runtime properties of 
the concurrency layer including deadlines and scheduling policies.
We provide an implementation of ABS concurrency layer as a Java API library 
and framework utilizing the latest langauge additions 
in Java 8~\cite{jsr335:lambda:translation}.
We design a large-scale monitoring system as a real-world application; 
the monitoring system is built with actors and ABS concurrency 
with formal semantics of ABS composed with 
schedulability analysis~\cite{fersman2007task}.
We elaborate on the elements of this research in the following.

>>>>

The core contributions of this thesis target at the intersection of object 
orientation, actor model, and concurrency.
We choose Java as the main programming language and as one of the mainstream 
object-oriented languages. 
We formalize a subset of Java and its concurrency API~\cite{jsr166} to 
facilitate formal verification and reasoning about it.
We create an abstract mapping from a concurrent-object modelling language, 
ABS~\cite{johnsen2012abs}, to programming semantics of Java concurrency. 
We provide the formal semantics of the mapping and runtime properties of 
the concurrency layer including deadlines and scheduling policies.
We provide an implementation of ABS concurrency layer as a Java API library 
and framework utilizing the latest langauge additions 
in Java 8~\cite{jsr335:lambda:translation}.
We design and implement a runtime monitoring framework, JMSeq, to verify the
sequenced execution of methods through code annotatinon in JVM. 
In addition, we design a large-scale monitoring system as a real-world 
application; the monitoring system is built with actors and ABS concurrency 
with formal semantics of ABS composed with schedulability 
analysis~\cite{fersman2007task}.
We elaborate on the elements of this research in the following.
